---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# odsR Package

This is an R package to facilitate the extraction of NHS organisation data from the
NHS Digital ODS API into the R environment

Any feedback would be appreciated and can be provided using the Issues section of the GitLab repository, or by emailing PHDS@phe.gov.uk

<br/>
<br/>

## Installation

#### From zip

Download this repository from GitLab and either build from source or do:

```{r source_pkg-installation, eval = FALSE}
source <- devtools:::source_pkg("C:/path/to/odsR-master")
install(source)
```

#### With devtools

You can install the latest version of odsR from GitLab with:

```{r gl-installation, eval = FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_git('https://gitlab.phe.gov.uk/georgina.anderson/odsR', build_vignettes=TRUE)
```

<br/>
<br/>


## Package Versioning
Following installation of this package, type 'packageVersion("odsR")' in the R console to show the package version.  If it is suffixed with a 9000 number then you are using an unapproved development version.

Released versions of this package will have version numbers consisting of three parts: <major>.<minor>.<patch>
In-development versions of this package will have a fourth component, the development version number, which will increment from 9000.

See http://r-pkgs.had.co.nz/description.html for further information on package versioning


## Package Contents
The package contains the following functions - see individual item documentation for full details 

**Functions:**  
- getODS   (get summary organisation data for multiple organisations)
- getODS1  (get full organisation data for a single organisation - not yet included)
- getODSsync (get organisation API urls for any organisations whose details have changed since a specific date - not yet included)

**Datasets:**  
- none

**Vignettes:**  
- none


