---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# odsR Package

This is an R package to facilitate the extraction of NHS organisation data from the
NHS Digital ODS API into the R environment.   

Any feedback would be appreciated and can be provided using the Issues section of the GitHub repository, or by emailing PHDS@phe.gov.uk.  Please note that whilst we are happy to share this package we have limited capacity to invest time in its further development.


<br/>
<br/>

## Installation

#### From GitHub

You can install the latest version of odsR from GitHub with:

```{r gh-installation, eval = FALSE}

# install.packages("devtools")
devtools::install_github("https://github.com/PublicHealthEngland/odsR",
                         build_vignettes = TRUE,
                         dependencies = "suggests")


# you may need to install and load the httr library and then execute the code below 
# note that this removes verification of authenticity of the peer's certificate 
httr::set_config(config(ssl_verifypeer = 0L))

```

#### From zip

Download this repository from Git and either build from source or do the following:

```{r source_pkg-installation, eval = FALSE}

# install.packages("devtools")
source <- devtools:::source_pkg("C:/path/to/odsR-master")
install(source)
```


#### Using Base R
To install the package without the use of devtools, download the .tar.gz file and then run:

install.packages(path_to_file, repos = NULL, type="source")
Where path_to_file would represent the full path and file name


<br/>
<br/>


## Package Versioning
Following installation of this package, type 'packageVersion("odsR")' in the R console to show the package version.  If it is suffixed with a 9000 number then you are using an unapproved development version.

Released versions of this package will have version numbers consisting of three parts: <major>.<minor>.<patch>
In-development versions of this package will have a fourth component, the development version number, which will increment from 9000.

See http://r-pkgs.had.co.nz/description.html for further information on package versioning


## Package Contents
The package contains the following functions - see individual item documentation for full details 

**Functions:**  

RELEASED:  

- getODS      (get summary organisation data for all organisations that meet the specified filter criteria)
- getODSfull  (get full organisation data for a single organisation)

IN DEVELOPMENT:  

- AddOrgName (insert an Organisation Name column to a data frame that contains Organisation Codes)
- OrgRelLkp  (create lookup tables from one organisation type to another based on relationship information held within the ODS API)

**Datasets:**  
- none

**Vignettes:**  
- none


